---
title: "Markdown for exam project for Introduction to Cultural Data Science"
author: "Otto Sejrskild Santesson, study ID: 202004347"
date: "12th of January, 2023" 
output: 
  html_document:
    toc: true
    toc_float: true
    highlight: tango
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Loading in packages needed for the project (some might be redundant, but it doesn't affect the 
# R environment in this case)
pacman::p_load(utils,tidyverse, patchwork, ggplot2, lme4, stats, grid, ggpubr, ggrepel, graphics,effects,VCA, vroom, readbulk,stringi, gridExtra, MuMIn,dfoptim, reticulate, Rcpp,dplyr, pacman,lmerTest,boot, dagitty,rstan,rethinking,truncnorm,jsonlite, devtools, coda, mvtnorm, devtools, loo, cmdstanr, ggdag)
```
### Source and rigin of the data employed
The data has been fetched online from Global Health Data Exchange (GHDX), which on their website is described at "the world’s most comprehensive catalog of surveys, censuses, vital statistics, and other health-related data". GHDX is part of the Institute for Health Metrics and Evaluation (IHME), which is an independent global health research center at the University of Washington. 

Concretely, the data is from the results of the 2019 Global Burden of Disease (GBD) study, and was accessed using the following link: https://vizhub.healthdata.org/gbd-results. The data was acquired the on the 9th of January 2023.

The search criterias applied are as follows:
GBD Estimate: ‘Cause of death of injury’
Measure: ‘Prevalence’
Metric: ‘Number’ & ‘Percent’ & ‘Rate’
Cause: ‘Mental disorders’
Location: ‘All countries and territories” (The state 'Georgia' of the United States of America was deselected, since otherwise it will not be possible to discern between the state and the country Georgia)
Age: '10-24'
Sex: 'Both' (i.e. male and female)
Year: All available years, from 1990 to 2019


```{r Loading in the data}
# Setting my work directory to my local repository
setwd("/Users/ottosejrskildsantesson/Desktop/Cultural Data Science/Cultural Data Science Rproject/AU668917_santesson_otto/exam_project/")

# Loading in the above-mentioned data from the data folder 
df = read_csv("data/raw_GBD_data.csv")

# Listing the column names, so the adequate meta data can be provided (what the different column names mean)
colnames(df)
```
### Variable/column information:
- 'measure': Name of the measure chosen (multiple options were available when filtering the data, using the database provided above). All of the values for this column is 'Prevalence'.
- 'location': Name of the country or territory
- 'sex': Specifies the sex of the data point - it is 'Both' for all of the data points, meaning that the data doesn't specify the sex (it is both female and male)
- 'age': Specifies the age grouping of the data point (all of the data points has the age group 10-24 years old)
- 'cause': The number ID of the disease - all of the values of this column is 'Mental disorders'
- 'metric': Specifies the specific metric used for the specific data point/row - 'Number' specifies the absolute number of cases of mental disorders in the specified age group of the given country/territory, 'Percent' specifies the percentage of the specific population (country and age) that has a mental disorder and 'Rate' specifies the change from year to year
- 'year': Specifies the year of the data
- 'val': Specifies the mean of the estimate - since there is some uncertainty with the exact pervasiveness of mental disorders, the data includes three column representing the estimate, where the 'val' column specifies the mean estimate
- 'upper: Specifies the upper bound of the uncertainty interval of the estimate, which is the 97.5 % percentile estimate
- 'lower': Specifies the lower bound of the uncertainty interval of the estimate, which is the 2.5 % percentile estimate

### Data wrangling and preparement of data frames
```{r Constructing the data frame for map plotting}
# Loading in the map data frame object - essential for plotting data on maps
mapdata = map_data("world")

# The countries of the two data frames (df, containing the data of the prevalence of mental disorder, and mapdata, containing the geographical mappings of the country) are not fully aligned in the sense that the assigned names are different, e.g. "United States of America" in df and "USA" in mapdata. This will be rectified in an unsophisticated yet straightforward manner in the following lines of code:
df$location = ifelse(df$location == "Micronesia (Federated States of)", "Micronesia", df$location)
df$location = ifelse(df$location == "United States of America", "USA", df$location)
df$location = ifelse(df$location == "United Kingdom", "UK", df$location)
df$location = ifelse(df$location == "Republic of Korea", "South Korea", df$location)
df$location = ifelse(df$location == "Democratic People's Republic of Korea", "North Korea", df$location)
df$location = ifelse(df$location == "Czechia", "Czech Republic", df$location)
df$location = ifelse(df$location == "Micronesia (Federated States of)", "Micronesia", df$location)
df$location = ifelse(df$location == "Republic of Moldova", "Moldova", df$location)
df$location = ifelse(df$location == "Viet Nam", "Vietnam", df$location)
df$location = ifelse(df$location == "Iran (Islamic Republic of)", "Iran", df$location)
df$location = ifelse(df$location == "United Republic of Tanzania", "Tanzania", df$location)
df$location = ifelse(df$location == "Venezuela (Bolivarian Republic of)", "Venezuela", df$location)
df$location = ifelse(df$location == "Taiwan (Province of China)", "Taiwan", df$location)
df$location = ifelse(df$location == "Russian Federation", "Russia", df$location)
df$location = ifelse(df$location == "Brunei Darussalam", "Brunei", df$location)
df$location = ifelse(df$location == "Lao People's Democratic Republic", "Laos", df$location)
df$location = ifelse(df$location == "Bolivia (Plurinational State of)", "Bolivia", df$location)
df$location = ifelse(df$location == "Syrian Arab Republic", "Syria", df$location)
df$location = ifelse(df$location == "Côte d'Ivoire", "Ivory Coast", df$location)
df$location = ifelse(df$location == "Cabo Verde", "Cape Verde", df$location)
mapdata$region = ifelse(mapdata$region == "Swaziland", "Eswatini", mapdata$region)
mapdata$region = ifelse(mapdata$region == "Trinidad" | mapdata$region == "Tobago" , "Trinidad and Tobago", mapdata$region)
mapdata$region = ifelse(mapdata$region == "Antigua" | mapdata$region == "Barbuda" , "Antigua and Barbuda", mapdata$region)
mapdata$region = ifelse(mapdata$region == "Saint Vincent" | mapdata$region == "Grenadines" , "Saint Vincent and the Grenadines", mapdata$region)
mapdata$region = ifelse(mapdata$region == "Saint Kitts" | mapdata$region == "Nevis" , "Saint Kitts and Nevis", mapdata$region)
mapdata$region = ifelse(mapdata$region == "Virgin Islands" & grepl("US", mapdata$subregion) == TRUE , "United States Virgin Islands", mapdata$region)

# Filtering in the df, since we only need the metric of 'Percentage' for the data visualization:
df_filtered = df %>% filter(metric == "Percent")

# Changing the 'val' column (percentage of 10-24 year olds with mental disorder) from being represented in decimals to percentage 
df_filtered$val = df_filtered$val*100

# Filtering the df, so it only includes countries/regions that are in the 'mapdata' dataframe (thus filtering out all of the redundant regions, such as the individual states of USA)
df_filtered = df_filtered[df_filtered$location %in% mapdata$region,]

# Now joining the two data frames together, so it is ready to be plotted
joined_frame = left_join(mapdata, df_filtered, by = c("region" = "location"))

# Filtering the data frame, so we only include the countries/regions that we have data on:
filtered_joined_frame = joined_frame %>% filter(!is.na(joined_frame$val))
```

```{r Fixing the data for Kosovo and adding it to the filter_joined_frame}
# So, if we plotted the data from filtered_joined_frame on a map, then there would be a blank spot where Kosovo is supposed to be, since the raw data doesn't include any data on Kosovo. This is preferably avoided, so we construct a data frame for Kosovo that is compatible with the other data:

# Starting off by filtering, so we only get rows where the region is "Kosovo"
joined_frame_kosovo = joined_frame %>% filter(region == "Kosovo")

# We make a variable that is equal to the length of the Kosovo-filtered data frame, which is gonna be used in a moment
rep_number = nrow(joined_frame_kosovo)

# We now make a vector with the different years
years <- seq(from = 1990, to = 2019)

# We now extend the Kosovo-filtered data frame by repeating the rows with the number of years
joined_frame_kosovo <- joined_frame_kosovo[rep(1:nrow(joined_frame_kosovo), each = length(years)), ]

# We add on the values for 'year' column
joined_frame_kosovo$year = rep(years, rep_number)

# And finally, we add the data frame to the main data frame defined in the previous chunk
filtered_joined_frame = rbind(filtered_joined_frame, joined_frame_kosovo)
```


```{r Filtering data frames for the visualization}
# Preparing the data frame for Denmark is very simple - we simply just specify the region to be "Denmark"
filtered_joined_frame_dk = filtered_joined_frame %>% filter(region == "Denmark")

# To prepare the data frame for the visualization of the European countries, we first start of by defining a vector with the European countries
european_countries = c("Albania", "Andorra", "Armenia", "Austria", "Azerbaijan",
  "Belarus", "Belgium", "Bosnia and Herzegovina", "Bulgaria", "Croatia",
  "Cyprus", "Czech Republic", "Denmark", "Estonia", "Finland", "France",
  "Georgia", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Italy",
  "Kazakhstan", "Kosovo", "Latvia", "Liechtenstein", "Lithuania", "Luxembourg",
  "North Macedonia", "Malta", "Moldova", "Monaco", "Montenegro", "Netherlands",
  "Norway", "Poland", "Portugal", "Romania", "San Marino", "Serbia",
  "Slovakia", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "Ukraine",
  "UK", "Vatican City", "Russia")

# We then filter the main data frame, by specifying that the region has to be in the vecotr of European countries specified above
filtered_joined_frame_eu = filtered_joined_frame %>% filter(region %in% european_countries)

# To prepare the data frame for the data vizualisation of all of the world countries, nothing has to be done - the data frame is simply 'filtered_joined_frame'
```


### Plotting
```{r Plotting animate map plot, Denmark}
# Initializing 'gganimate' an R package that allows us to animate our ggplots, so we can see the development over time. We also need to initialize another package in order for it to run:
pacman::p_load(gganimate,transformr, gifski, png)

animated_map_plot_dk = ggplot(filtered_joined_frame_dk) + # Initializing the basis of the ggplot
  geom_polygon(aes(x = long, y = lat, group = group, fill = val), color = "black") + # Filling out with respect to the percent of mental disorders
  transition_time(year) + # Needed for the animation of the plot - telling it, that it should animate with respect to 'year'
  scale_fill_gradient(name = "% mental disorder", low = "#FFF04D", high =  "darkred", na.value = "grey50") + # Defining the gradient for the fill color
  theme(axis.text.x = element_blank(), # Making the plot more neat, by removing uninformative graphic settings
        axis.text.y = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())+
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, Denmark") + # Setting up the title
  labs(subtitle = "Year: {round(frame_time,0)}") # Setting up a subtitle that is matched with what year it is 

# Plotting the plot
animated_map_plot_dk
```


```{r Plotting animate bar plot, Denmark}
# A different way to visualize the data in an animated fashion; using a barplot
animated_bar_plot_dk = df_filtered %>% 
  filter(location == "Denmark") %>% 
  ggplot(., aes(location, val)) +
  transition_time(year) +
  geom_col(fill = "darkred", color = "white", width = 0.25) +
  guides(fill = FALSE) +
  scale_y_continuous(breaks = seq(from = 0, to = max(18), by = 1)) +
  ylab("Percentage") +
  theme(axis.title.x = element_blank()) +
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, Denmark") +
  labs(subtitle = "Year: {round(frame_time,0)}")

animated_bar_plot_dk
```


```{r Plotting animate map plot, Europe}
animated_map_plot_eu = ggplot(filtered_joined_frame_eu) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = val), color = "black") + # Filling out the countries in respect to the percent of mental disorders
  transition_time(year) +
  scale_fill_gradient(name = "% mental disorder", low = "#FFF04D", high =  "darkred", na.value = "grey50") + 
  coord_cartesian(xlim = c(-25, 45), ylim = c(32,72)) + # Cropping the map, so it looks neater
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())+
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, Europe") + 
  labs(subtitle = "Year: {round(frame_time,0)}")

animated_map_plot_eu
```


```{r Plotting animate bar plot, Europe}
animated_bar_plot_eu = df_filtered %>% 
  filter(location %in% european_countries) %>% 
  ggplot(., aes(location, val)) +
  transition_time(year) +
  geom_col(fill = "#001489", color = "white") +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(axis.text.x = element_text(size = rel(0.90))) +
  scale_y_continuous(breaks = seq(from = 0, to = 28, by = 1)) +
  ylab("Percentage") +
  theme(axis.title.x = element_blank()) +
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, Europe") +
  labs(subtitle = "Year: {round(frame_time,0)}")

animated_bar_plot_eu
```


```{r Plotting animate map plot, Denmark, World}
animated_map_plot_world = ggplot(filtered_joined_frame) + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = val), color = "black") +
  transition_time(year) +
  scale_fill_gradient(name = "% mental disorder", low = "#FFF04D", high =  "darkred", na.value = "grey50") + 
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())+
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, World") +
  labs(subtitle = "Year: {round(frame_time,0)}")

animated_map_plot_world
```


```{r Plotting animate bar plot, World}
# Since it is all of the worlds countries that have to fit on the x-axis, the plot is going to be very cluttered.
animated_bar_plot_world = df_filtered %>% 
  filter(location %in% joined_frame$region) %>% 
  ggplot(., aes(location, val)) +
  transition_time(year) +
  geom_col(fill = "#242526", color = "white") +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(axis.text.x = element_text(size = rel(0.5))) +
  scale_y_continuous(breaks = seq(from = 0, to = 28, by = 1)) +
  ylab("Percentage") +
  theme(axis.title.x = element_blank()) +
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, World") +
  labs(subtitle = "Year: {round(frame_time,0)}")

animated_bar_plot_world
```


```{r Plotting still plots}
# Since it is not possible to show animated plots on a PDF, I will make some additional (still) plots to put into the assignment:

# A plot showing the development of the percentage of 10-24 year olds with mental disorder in Denmark from 1990 to 2019
 ggplot(filtered_joined_frame_dk, aes(year, val, color = val)) + # Mapping 'color' to 'val', so we can visualize the development with colors as well
  geom_line()+ # Using the line geom to visualize the data
  scale_color_gradient(low = "#FF8308", high = "#C6080C") + # Defining the gradient color
  scale_x_continuous(breaks = seq(from = 1990, to = 2019, by = 1))+ # Making some more ticks on the x-axis, so the plot is more legible
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # Adjusting the angels of the labels on the x-axis
  coord_cartesian(xlim = c(1991.28, 2017.72))+ # Hardcoding the limits of the x-axis, so it is exactly how we want it (otherwise, there would be some ugly spacing)
  guides(color = FALSE) + # Removing the legend, since it is redundant
  xlab("Year") + # Renaming the x- and y-axis
  ylab("Percentage")+
  ggtitle("Percentage of mental disorders among 10-24 year olds in Denmark, from 1990 to 2019")+ # Defining our plot title
  theme(plot.title = element_text(size = rel(1.05))) # And finally adjusting the size of it - otherwise, the title wouldn't fit the plot


# Making the map plots from before, but only with the 2019 data:
# Denmark
ggplot(filter(filtered_joined_frame_dk, year == 2019)) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = round(val,2)), color = "black") + 
  scale_fill_gradient(name = "% mental disorder", limits = c(16,18), low = "#FFF04D", high =  "darkred", na.value = "grey50") +
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())+
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, Denmark") +
  labs(subtitle = "Year: 2019")

# Europe
ggplot(filter(filtered_joined_frame_eu, year == 2019)) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = round(val,2)), color = "black") + 
  scale_fill_gradient(name = "% mental disorder", low = "#FFF04D", high =  "darkred", na.value = "grey50") +
  coord_cartesian(xlim = c(-25, 45), ylim = c(32,72)) +
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())+
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, Europe") +
  labs(subtitle = "Year: 2019")

# World
ggplot(filter(filtered_joined_frame, year == 2019)) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = round(val,2)), color = "black") + 
  scale_fill_gradient(name = "% mental disorder", low = "#FFF04D", high =  "darkred", na.value = "grey50") +
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())+
  labs(title = "Proportion of 10-24 year olds, who have a mental disorder, World") +
  labs(subtitle = "Year: 2019")



# Making the bar plots from before, but only with the 2019 data:
# Europe
df_filtered %>% 
  filter(location %in% european_countries) %>% 
  filter(year == 2019) %>% 
ggplot(., aes(location, val)) +
  geom_col(fill = "#001489") +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(axis.text.x = element_text(size = rel(0.90))) +
  ylab("Percentage") +
  theme(axis.title.x = element_blank()) +
    labs(title = "Proportion of 10-24 year olds, who have a mental disorder, Europe") +
  labs(subtitle = "Year: 2019")

# World
# Be aware - since it is all of the countries of the world, the plot is going to be very cluttered. There is no way around it 
df_filtered %>% 
  filter(location %in% joined_frame$region) %>% 
  filter(year == 2019) %>% 
ggplot(., aes(location, val)) +
  geom_col(fill = "#242526", color = "white") +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(axis.text.x = element_text(size = rel(0.5))) +
  ylab("Percentage") +
  theme(axis.title.x = element_blank()) +
    labs(title = "Proportion of 10-24 year olds, who have a mental disorder, World") +
  labs(subtitle = "Year: 2019")
```
