---
title: "3:W35: Start with R - Homework for Cultural Data Science"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Just a bunch of packages, that I keep on adding to every time I run into a package that I need to use (not good code practice)

pacman::p_load(utils,tidyverse, patchwork, ggplot2, lme4, stats, grid, ggpubr, ggrepel, graphics,effects,VCA, vroom, readbulk,stringi, gridExtra, MuMIn,dfoptim, reticulate, Rcpp,dplyr, pacman,lmerTest,boot, dagitty,rstan,rethinking,truncnorm)
```


## Exercise #1
```{r}
rooms <- c(1, 2, 4, 5, 1, 3, 1, NA, 3, 1, 3, 2, 1, NA, 1, 8, 3, 1, 4, NA, 1, 3, 1, 2, 1, 7, 1, 9, 3, NA)

which(rooms>2) %>% # First, we take the which() command to find out the indices of which of the elements that are greater than 2. This will result in a new vector, with the indices of all of the aforementioned elements
rooms[.] %>%  # We then use this vector of indices to get out the actual elements that are greater than 2 from the 'rooms' vector
length() # Then we take the length of this vector, to see how many elements (that are greater than 2) there are.
```
We can conclude, that there are 12 elements in the rooms vector that are greater than 2.

Now we go on with finding the sum of the elements found above:
```{r}
# We start out by just repeating the first few steps from above, and instead of using the length()-function, we utilize the sum()-function. This function takes all of the elements of the vector and sum them together:

which(rooms>2) %>% 
  rooms[.] %>% 
  sum()
```
We find, that the sum of the elements greater than 2 in the 'rooms' vector is 55.

## Exercise #2

In order to determine which type/class the data is in the 'rooms' vector, we perform the following line of code:
```{r}
class(rooms) # Easy peasy lemon squeezy 
```
We can conclude, that the data of the 'rooms' vector are numeric (i.e. they're numbers)

## Exercise #3
See attached file/file uploaded to GitHub



