---
title: "3:W35: Start with R - Homework for Cultural Data Science"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Just a bunch of packages, that I keep on adding to every time I run into a package that I need to use (not good code practice)

pacman::p_load(utils,tidyverse, patchwork, ggplot2, lme4, stats, grid, ggpubr, ggrepel, graphics,effects,VCA, vroom, readbulk,stringi, gridExtra, MuMIn,dfoptim, reticulate, Rcpp,dplyr, pacman,lmerTest,boot, dagitty,rstan,rethinking,truncnorm)
```


## Exercise #1
```{r}
rooms <- c(1, 2, 4, 5, 1, 3, 1, NA, 3, 1, 3, 2, 1, NA, 1, 8, 3, 1, 4, NA, 1, 3, 1, 2, 1, 7, 1, 9, 3, NA)

which(rooms>2) %>% # First, we take the which() command to find out the indices of which of the elements that are greater than 2. This will result in a new vector, with the indices of all of the aforementioned elements
rooms[.] %>%  # We then use this vector of indices to get out the actual elements that are greater than 2 from the 'rooms' vector
length() # Then we take the length of this vector, to see how many elements (that are greater than 2) there are.
```
We can conclude, that there are 12 elements in the rooms vector that are greater than 2.

Now we go on with finding the sum of the elements found above:
```{r}
# We start out by just repeating the first few steps from above, and instead of using the length()-function, we utilize the sum()-function. This function takes all of the elements of the vector and sum them together:

which(rooms>2) %>% # Doing the same as above
  rooms[.] %>% # The period just denotes the things that comes from the pipe above
  sum() # Taking the sum of it all
```
We find, that the sum of the elements greater than 2 in the 'rooms' vector is 55.

## Exercise #2

In order to determine which type/class the data is in the 'rooms' vector, we perform the following line of code:
```{r}
class(rooms) # Easy peasy lemon squeezy 
```
We can conclude, that the data of the 'rooms' vector are numeric (i.e. they're numbers)

## Exercise #3
```{r}
download.file("https://ndownloader.figshare.com/files/11492171","data/SAFI_clean.csv", mode = "wb")
interviews = read_csv("data/SAFI_clean.csv")
view(interviews)
```
Link to the photo on GitHub: https://github.com/Digital-Methods-HASS/AU668917_santesson_otto/blob/main/r_screenshot_environment.png


## Exercise #4 
```{r message = FALSE}
# We start of by making the data frame ready for the required analysis
kings = read_csv2("danish_monarchs.csv") %>%  # Loading in the group-made csv-file
  as_tibble() %>% # Turning it into a tibble
  select(1:7) %>% # Selecting the first seven rows, since the last to rows (8 & 9) are empty columns
  mutate(reigned_years = end_reign-start_reign) %>% # Adding a column that specify the reigned years
  mutate(reigned_days = (reigned_years %/% 4)*366 + (reigned_years - (reigned_years %/% 4))*365) %>% # Adding a column that specify the total reigned days (taking transition years into account, by making a rough estimate)
  filter(!is.na(reigned_days)) # We omit Margrethe the Second, since she is still in her reign, and taking the period of her current reign wouldn't be representative. 


# We're now ready to perform the analysis on the tibble/column of interest (reigned_days)
paste("The mean of rule over time of the Danish monarchs is",round(mean(kings$reigned_days), 2),"days")
paste("The median of rule over time of the Danish monarchs is",median(kings$reigned_days),"days")

# To find the three monarchs who ruled the longest, we perform the following operations on the tibble:
kings %>% arrange(desc(reigned_days)) %>% # Arranging the tibble with regards to who has greatest value in the 'reigned_days' column, from greatest to lowest
  .[1:3,] %>% # Taking the top three rows (monarchs) - the period denotes the tibble coming from the preceding pipe
  select(Monarch,reigned_days) # We end up by taking the two essential columns we need in order to answer our inquiry
```
We see, that Christian 4. had the longest rule of all the Danish Monarchs. Erik 7. af Pommern and Christian 9. share the second place, with equally long periods of rule (this is of course not accurate, but the best estimate that could be made with the limited data available)
